\subsection{Path Dependency and Lock-in} \label{sec:path-depenency}
Path dependency is an economic theory, which explains how history or past decision influences the present. The choices we made in the past influences the choices we make today. This holds for the continuous use of a standards, products or practices. Path dependence is caused by the behavior of doing things the way we know, out of uncertainty about the cost of alternatives, because the cost of conversion exceeds the immediate gains in operating efficiency. This way, we are locked in with suboptimal technology or inferior standard even though a more efficient one is available, as short-run benefits often outweighs the long-run benefits. As Douglas North said: \textit{``Once a development path is set on a particular course, the network externalities, the learning process of organizations, and the historically derived modelling of the issues reinforces the course.’’}

There exist three degrees of path dependence as defined by \cite{Liebowitz2001WinnersTechnology}:
\begin{itemize}[noitemsep]
    \item First-degree Path Dependence -- decisions made in the past, based on correct predictions about the future however, the position in which the individual is now because of the decision may not seem optimal. Though, there is no error or inefficiency.
    \item Second-degree Path Dependence -- the individual makes decisions based on information available at the moment which may be imperfect and therefore it led to a situation which is regrettable and not optimal at the moment and costly to change. Still, no inefficiency is present.
    \item Third-degree Path Dependence -- decision based on available information leads to not optimal results, even though other alternatives were present, which would lead to better outcome, given the information available at the moment.
\end{itemize}
  
Lock-in occurs when a switching from one vendor, standard or a practice to a another comes with a substantial switching cost, making it inefficient to change and become dependent.

\paragraph{Path dependency and Lock-in effect on cloud-based machine learning services}

As for every business, there is a company offering a service or a product and customers on the other side. Therefore, this theory will be applied, and dependencies defined for both sides.

From the Microsoft’s point of view, as the company offering a service, two important dependencies are defined. First arise, when the company invests in developing a software solution which become available for customers as a service. It is put on the market, many customers are using it however, it is found out that it is buggy and therefore need costly maintenance. \acrshort{ms} has two options, either keeping the buggy service up for use and paying for maintenance or develop a new service, which will be better but the switching cost higher than current maintenance. 

Another dependency is the hardware one, where the company makes an agreement or partnership with a supplier for the hardware needed to host its services. But if the hardware does not perform to expectations or is too buggy, it will cause the company either a big switching cost to a new hardware or a lot of money for maintenance. 

From the customer’s point of view, a developer may use the service for free to try to develop a machine learning algorithm, but as it becomes more complex, they needs more resources and need to make a decision whether to continue using \acrshort{ms}’s services and pay for them or switch to a competition. At the early phases of development, the switching cost are not high, but if the development team becomes dissatisfied with the service once the solution has been developed, the switching cost are too high. Similarly, it works with bundles that \acrshort{ms} offers with their \acrshort{ml} studio. The customer may only be interested in using one particular service from the bundle for the implementation, but they may eventually end up using more of the services as they are part of the solution and customers becomes locked-in to the solution. 